Implications of afforestation policies for global markets

### 2024-02-25 paper.Rmd
Update paper.Rmd

@@

>>>>

1a) On aggregate zero percent net deforestation Globally

@@

# Results
We first examined the impact of a scenario where the rate of deforestation globally was reduced to zero through the implementation of a uniform global tax rate on the conversion of forestland to agricultural land. A tax rate of roughly 70 percent was required to achieve this. With this policy in place, most regions of the world would see significant declines in the amount of agricultural land in 2030 relative to the baseline scenario where land conversion was not taxed. For the United States, agricultural land would be 2.1 percent less (Table 1). Larger decreases would happen in important regions such as Brazil (-9.7 percent), the rest of South America (-14.7 percent), Southeast Asia (-10.0 percent), and Sub-Saharah Africa (-4.8 percent).

Table 1
	                              ∆ (%)
Central America	                -16.9
East Asia	                      -14.4
North Africa & the Middle East	-11.1
Southeast Asia	                -10.0
Russia	                        -9.8
Brazil	                        -9.7
Rest of South America	          -14.7
South Asia	                    -9.1
Canada	                        -8.1
Oceania	                        -7.5
European Union	                -6.4
Sub-Saharan Africa	            -4.8
EUII	                          -3.3
China	                          -2.5
United States	                  -2.1
Japan	                          11.4
